### 2021-03-08 paper/rebuttal/rebuttal.tex

\subsection{Changes to the manuscript}
To reflect these additional experiments, we have made the following changes to our manuscript:
\begin{itemize}
	\item Re-drawn figures with embeddings using $\gamma = 1.0$, and included performance differences in Fig.~\ref{fig:supp:hyperparameter}, which was added to the supporting materials.
	\item Added Fig~\ref{fig:supp:distancemetrics} and Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table} to the manuscript.
	\item We have added sentence speculating on SGD performance differences into supporting materials
\end{itemize}

%
% SECTION- POINT-BY-POINT DISCUSSION
%
\clearpage
\section{Point-by-point response}
All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript. Here we offer further discussion, and introduce several results and figures to support certain arguments.
\todo{@dakoda, could you check the numbering comment from yy?}
\subsection{Response to Referee 1}

@@

\response{Thank you for this comment. While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts. This is confirmed in extra work done in response to these reviews.

	We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical.
	In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$.
	We found that while performance varies across each combination of parameters, the main results remain qualitatively similar.
	While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.

	We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust.
	About 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:

	“We note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories). Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random fluctuations.”

@@

}

\rcomment{%
	Another interesting point in this work is that the authors chose to not report p-values or the results of statistical significance tests (except confidence intervals). I presume this was a conscious decision, which I do not necessarily agree with. I see no critical error in the approach used by the authors, but I would have found aspects of the manuscript easier to understand in places with results of statistical tests (e.g., associated with goodness-of-fit tests formally test that the embedding-based distances are more correlated with the flux values). Given the sample sizes involved, I have no doubt that the results are statistically significant. However, I personally do see value in rigorously performed frequentist hypothesis testing, and I felt that this manuscript could be improved by employing such techniques.

	Lastly, the authors do not actually state how the 99 confidence intervals were constructed. (E.g., was this via a bootstrap approach?) This detail should be added.
}

\response{Thank you for this feedback.
	You are correct that it was a conscious choice to not report statistical significance in the form of a $p$-value.
	The use of statistical significance is contentious, and Nature itself has hosted some of this debate~\autocite{amrhein2019statistics}.
	As such, we avoided $p$-values in our research when it made sense to do so.
	In our analysis, all significance levels were below 0.0001, with most computationally indistinguishable from zero.
	However, we recognize that $p$-values can help readers interpret results.
	As such, we have opted to add to a sentence such as \say{\textit{Correlation is calculated on the data in the log-log scale ($p < 0.0001$ across all fits)}.} or similar to relevant figures in the main text and supporting materials.

@@

%
% Response to reviewer 2
%
\clearpage
\subsection{Response to Referee 2}

\rcomment{%
	Although the paper is well written and explores a very interesting problem, I have certain criticism for the used methodology. After obtaining a representation of each dataset, the authors defined an embedding distance as the cosine distance between vectors in the space, while defining distance as the geographical distance in the original, spatially embedded datasets. Subsequently they used the Gravity Law to estimate the flux between location pairs of vector pairs in the spatial and embedded space respectively. The Gravity Law, applied on mobility, assumes that the number of people moving between two populations is proportional to the multiplicative of the sizes of the populations and a deterrence function. Research during the last decades on transportation, spatial networks and human mobility suggests that this deterrence function may take a functional form of an inverse exponential or an inverse power-law, as it has been acknowledged by the authors. However, the emergence of these different deterrence functions can be due to fundamentally different mechanisms (for a review on the topic see Barthélemy, Physics Reports 499, 1, 2011, a paper not cited in the manuscript). For example, the different cost functions (linear or logarithmic) to create link at a given distance, the spatial granularity of the observation, or even the heterogeneity of the moving individuals in terms of various factors, just to mention a few examples. Instead, the authors of the actual paper arbitrarily assumed a power-law deterrence function in the spatial case and an exponential deterrence function in the embedding space without further arguing their choice (other than fitting on the data). Furthermore, assuming different deterrence functions for the flux estimation using Gravity Law makes the estimated fluxes incomparable, resulting the invalidation of results depicted in Figure 2.
}

\response{Thank you for pointing this out.
	We carefully read out the Barthélemy, Physics Reports 499, 1, 2011, and referenced it in our manuscript.
	Also, we report the performance of the flux estimation and prediction using different deterrence functions (see Section 2, above), finding that although the absolute values vary, the pattern doesn't change---the embedding distance robustly outperforms geographic distance regardless of the function used.
	We add the following line to the methods noting this point,

	\medskip
	\say{The decay function $f(r_{ij})$ defines the effect of distance, and so different decay functions can model fundamentally different mechanism [...] such as the cost functions for a given distance and the spatial granularity of the observation.
		For geographic distance, we define $f(r_{ij})$ as the standard power-law function, and for the embedding distance, we use the exponential function, selected as the best performing for each cases though there is no qualitative difference---the embedding distance outperforms geographic distance regardless of the type of gravity model used (see Supporting Information).}

	We find the article that geographical distance ﬁts well with the power-law decay function because power-based gravity model can be more suitable for analyzing large, complex, and scale-free spatial systems with long-range spatial memory, while exponential-based gravity model
	fits well with the simple system with no spatial memory~\autocite{chen2015distance}.
	However, the embedding distance fits well with the exponential decay function, perhaps demonstrating that the real-world spatial complexity of mobility is encoded in the \textit{word2vec} embedding space as simpler pairwise distances, likely resulting from underlying connection we established between \textit{word2vec} and the gravity model (see Section 1, above).

@@

	The application of the Word2Vec method on the studied trajectory sequences is not well explained. Without explaining the embedding method briefly in the main text the reader has no idea how to interpret the embedding distance, which is in the hear of the study.

}

\response{Thank you.
	We have added the following sentence to the introduction: “It works under the notion that a good representation should facilitate prediction, and so learns a mapping of target locations (words) that best predict locations that co-appear in the same trajectory (sentence).”

	In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model” (see Section 1, above).

@@

	What is notable about our findings, therefore, is that even though a model trained with $w = 1$ generates fewer training samples, it still outperforms settings with $w > 1$, which use more training samples, and which should capture higher-order structures in the data.
	We speculate that this is because the word2vec model with $w = 1$ is equvelant to the gravity model of mobility (see Section 1).
}

\rcomment{
	The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored. E.g. to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
	Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”. This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.

}
\response{
	Thank you for these comments.
	First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the best performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.

	A full search of the hyper-parameter space would certainly be interesting and useful, however we believe that set of hyper-parameters we considered here is sufficient to establish the utility of the approach, and demonstrate that performance is only slightly different based on different hyper-parameters.
	There are previous studies on the optimal dimensionality of word embedding \autocite{yin2018understand, yin2018dimensionality}. Also, 
	we note that in previous work from our group, we explored the optimal dimensions for graph embedding~\autocite{gu2020dimensions}, finding that while a sufficient number of dimensions is necessary to capture the structure, increasing the dimensions does not detract from performance, a property common across deep learning methods.
	Given that there is little performance difference between $d = 100$ and $d = 300$, we opt to use the larger embeddings at $d = 300$, which are large enough to capture the complexity of mobility, yet small enough to allow an efficient computational workflow.
}

@@

\response{Thank you for this insightful comment!
	We think that there is a great deal of potential in methods like BERT for representing mobility data.
	What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches).
	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns such effective gravity-like relationships between entities (see Section 1, this letter).
	We believe hat this new discovery, now included in the manuscript, justifies our use of \textit{word2vec} here.

	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered. Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most

	To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality.}}.

@@

\rcomment{
	My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility. The technical description addressed most of them. However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference? That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance? For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects? Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
}

\response{Thank you for this idea!
	We believe that this is an interesting topic and we hope to investigate it in the future.
	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
	This is certainly a topic that is in our mind for future study.
	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.

	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new result to the manuscript.
}

@@

\rcomment{
	Finally, one cannot escape the fact that COVID changes our mobility patterns. Many groups have used mobile phone data to explore these changes. I wonder, how would the pre-covid embeddings apply to post-covid mobility? Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
}

\response{This is an excellent idea, and one that we have been interesting in addressing as well.
	Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative.
	Publications are on a time lag, compared to actual events.
	For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one.
	As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
	We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.

	In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows.
	We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky \autocite{hamilton-etal-2016-diachronic}, to align embeddings trained on different data in order to quantify the changes in global mobility.
	We look forward to approaching this, as well as other exciting projects in the future.
}

@@

\end{landscape}

%
% RMSE TABLE --- Exponential model
%
\clearpage
\begin{landscape}

	\providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
	\providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
	\providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
	\providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}

	\begin{table}[ht]
		\caption{
			\textbf{Prediction error between actual and predicted mobility with exponential gravity model, by metrics and experimental parameters}.
			Each cell corresponds to the prediction error (measured with root mean squared error) between the real-world flux between scientific organizations and predictions made with the exponential form of the gravity model of mobility.
			The prediction error is shown for the embedding distance compared against baselines, subsets of mobility data, and definitions of organization population.
			The asterisk denotes the top-performing distance metric by column (lowest prediction error).
			Distance metrics are ordered from lowest prediction error to highest, based on global mobility with organization population defined using all mobile and non-mobile authors.
			``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
			population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
			``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
			Embedding distance, measured as the cosine distance between embedding vectors, results in better predictions of mobility than baselines in nearly every case, however Levy's factorization~\autocite{levy2014neural} perform better in the case of international and domestic only mobility when using raw frequency populations.
		}
		\label{supp:table:rmse_exp_table}
		\begin{centerbox}
			\begin{threeparttable}
				\small
				\setlength{\tabcolsep}{0pt}
				\begin{tabular}{l l l l l l l l l l}

### 2021-03-08 paper/rebuttal/rebuttal.tex

\AtEveryBibitem{%
 \clearfield{url}%
   \clearfield{month}%
 \clearfield{issn}%
 \clearfield{doi}%%
}

\addbibresource{rebuttal.bib}

%
% HEADER
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Nature---Response to Reviews}
\rhead{\thepage}
\chead{}

\newcounter{comment}[subsection]

%
% COLORBOX
%
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\newtcolorbox[list inside=toc]{sectionbox}[1]{colback=white,
 				       												 colframe=black,
 				       												 colbacktitle=white!50!gray,
 				       												 coltitle=black,
 				       												 fonttitle=\bfseries, 
 				       												 phantom=\refstepcounter{comment},
 				       												 title={Comment \arabic{section}.\arabic{comment}},
 				       												 list entry={Comment \arabic{section}.\arabic{comment}\quad}, breakable}

@@

\rcomment{
	P6Para3: “For THEIR purpose…”
}

\response{Thank you, we have corrected this mistake.
}

\rcomment{
	P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained. Considering it was derived by the authors in a very recent paper, no one will know what it is.
}

\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
}

%
% Response to referee 4
%
\clearpage
\setcounter{section}{3}
\subsection{Response to Referee 4}
\setcounter{section}{4}

### 2021-03-08 paper/rebuttal/rebuttal.tex

\subsection{\textit{word2vec} algorithm}
Imagine a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory. A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$.
Then, the skip-gram \textit{word2vec} learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
%
% MAIN W2V Equation
%
\begin{equation}
	{\cal J} = \frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log P(a_{t + \tau} \vert a_{t}), \label{eq:word2vec-obj}
\end{equation}
where,

%
% CONDITIONAL PROBABILITY EQ
%
\begin{equation}
	P(j \given i) = \frac{\exp(\vect{u}_j \cdot \vect{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
\end{equation}
where $\vect{v}$ and $\vect{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations. In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.
Due to its simplicity and performance, negative sampling is the most widely used strategy, which we also adopt in our study.

\subsection{An implicit bias in the negative sampling}

Although negative sampling is the most common approximation, it is a biased estimator~\autocite{Chia2010,Dyer2014} that does not yield the optimal embeddings in terms of the objective function, ${\cal J}$.
This bias in negative sampling turns out to be a critical piece that connects wor2vec and the gravity model.

Negative sampling trains {\it word2vec} using a binary classification task as follows.
For each target word $i$, we sample a context word $j$ from the given data and label it as positive, denoted by $Y_{j}=1$.
Then, we sample $k$ words $\ell$ from a noise distribution $p_0(\ell)$ and label them as negative, denoted by $Y_{\ell}=0$.
In \textit{word2vec}, the noise distribution is given by $p_0(\ell) \propto P^\gamma (\ell)$, where $P(j)$ is the fraction of $j$ in the data, and $\gamma$ is a hyper-parameter.
Then, for the sampled words, we fit a logistic regression model:
\begin{align}
	\label{eq:logistic-regress}
	P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) = \frac{1}{1 + \exp(-\vect{u}_j \cdot \vect{v}_{i})},
\end{align}
by maximizing the log-likelihood:
\begin{align}
	\label{eq:log-likelihood-logistic-regress}
	{\cal J}^{\text{NS}} = \sum_{i \in {\cal A}} \sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1; \vect{v}_{i}, \vect{u}_j) + (1-Y_{j}) \log P(Y_{j} = 0; \vect{v}_{i}, \vect{u}_j)\right],
\end{align}
where ${\cal D}$ is the set of all sampled context words.

An underappreciated fact is that maximizing ${\cal J}^{\text{NS}}$ does not guarantee
to yield the optimum embedding in terms of the original skip-gram word2vec objective function ${\cal J}$ even if we increase the training samples and iterations~\autocite{Chia2010,Dyer2014}.
To make this bias explicit, let us consider the unbiased variant of negative sampling, \ie the noise contrastive estimation (NCE)~\autocite{Chia2010,Dyer2014}.
NCE is an unbiased estimator for a probability model $P_m$ of the form:
\begin{align}
	\label{eq:nce-model}
	P_m(x) = \frac{ f(x) }{\sum_{ x' \in {\cal X}} f(x') },
\end{align}
where $f$ is the non-negative likelihood function of data $x$, and ${\cal X}$ is the set of all data.
This general form includes the word2vec model (Eq.~\eqref{eq:cond_prob_w2v}), where $f(x) = \exp(x)$ and $x = \vect{u}_j \cdot \vect{v}_{i}$.
NCE fits the probability model using a binary classification task in the same way as in negative sampling but using a Bayesian formalism for logistic regression.
Specifically, before the training, we know that $1$ in $1+k$ words is sampled from the given data, which can be modeled as prior probabilities
\begin{align}
	\label{eq:prior}
	P_0(Y_{j} = 1) = \frac{1}{k + 1},\quad P_0(Y_{j} = 0) = \frac{k}{k + 1}.
\end{align}
Using the Bayes rule, the posterior probability for $Y_{j}$ given word $j$ is given by
\begin{align}
	\label{eq:posterior}
	P\left(Y_{j} \vert j\right) = \frac{
		P\left(j \vert Y_{j}\right)P(Y_{j})
	}{
		P\left(j \vert Y_{j} = 0\right)P(Y_{j} = 0)
		+ P\left(j \vert Y_{j} = 1\right)P(Y_{j} = 1)
	}.
\end{align}
Bearing in mind that word $j$ is sampled from the given data if $Y_{j}=1$ and from the noise distribution $p_0$ if $Y_j = 0$.
Assuming that the given data is generated from the probability model to fit, the class-conditional probability, $P\left(j \vert Y_{j}\right)$, is given by
\begin{align}
	\label{eq:class-cond}
	P(j \vert Y_{j} = 1) & = P_m(\vect{u}_j \cdot \vect{v}_{i}),
	\quad
	P(j \vert Y_{j} = 0)  = p_0 (j).
\end{align}
Putting Eqs.~\eqref{eq:prior}, \eqref{eq:posterior} and \eqref{eq:class-cond} together, the posterior probability for $Y_j$ is given by
\begin{align}
	\label{eq:nce}
	P\left(Y_{j} = 1 \vert j\right) & =
	\frac{
		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)
	}{
		P_m(\vect{u}_j \cdot \vect{v}_{i}) / (k + 1)  + kp_0(j) / (k + 1)
	}                                          \\
	                                & = \frac{
		P_m(\vect{u}_j \cdot \vect{v}_{i})
	}{
		P_m(\vect{u}_j \cdot \vect{v}_{i})  + kp_0(j)
	},
\end{align}
which can be rewritten in form of sigmoid function:
\begin{align}
	\label{eq:nce}
	P\left(Y_{j}=1 \vert j\right) =
	 & = \frac{
		1
	}{
		1 + kp_0(j) / P_m(\vect{u}_j \cdot \vect{v}_{i})
	}           \\
	 & = \frac{
		1
	}{
		1 + \exp\left[ \ln kp_0(j) - \ln P_m(\vect{u}_j \cdot \vect{v}_{i}) \right]
	}           \\
	 & = \frac{
		1
	}{
		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i})  + \ln p_0(j) + c \right]
	},
\end{align}
where $c = \ln k + \ln\sum_{ x' \in {\cal X}} f(x') $ is a constant.
NCE maximizes the log-likelihood
\begin{align}
	\label{eq:log-likelihood-logistic-regress}
	{\cal J}^{\text{NCE}} = \sum_{i \in {\cal A}}\sum_{j \in {\cal D}} \left[ Y_{j} \log P(Y_{j} = 1\vert j) + (1-Y_{j}) \log P(Y_{j} = 0 \vert j)\right].
\end{align}
by calculating the gradients for embedding vectors $\vect{u}_j$, $\vect{v}_{i}$ and iteratively updating them.
An important consequence of this framework is that NCE is an unbiased estimator that has convergence to the optimal embedding in terms of the original word2vec's objective function, ${\cal J}$~\autocite{Chia2010,Dyer2014} if we increase the number of words to sample and the training iterations.

Let us revisit negative sampling from the perspective of NCE.
We rewrite the logistic regression model in negative sampling (Eq.~\eqref{eq:logistic-regress}) in form of the posterior probability:
\begin{align}
	P^{NS}\left(Y_{j}=1 \vert j\right) & = \frac{
		1
	}{
		1 + \exp\left[ - \left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c \right) + \ln p_0(j) + c \right]
	}                                             \\
	                                   & = \frac{
		1
	}{
		1 + \exp\left[ - \ln f(\vect{u}_j \cdot \vect{v}_{i}) + \ln p_0(j) + c \right]
	},
\end{align}
where we define the likelihood function $f$ by
\begin{align}
	f(\vect{u}_j \cdot \vect{v}_{i}) = \exp\left( \vect{u}_j \cdot \vect{v}_{i} + \ln p_0(j) + c\right),
\end{align}
which is the unbiased estimator for the probability model
\begin{align}
	\label{eq:unbiasef}
	P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i}) & = \frac{ f(\vect{u}_j \cdot \vect{v}_{i}) }{\sum_{ j' \in {\cal A}} f(\vect{u}_{j'} \cdot \vect{v}_{i}) },                                                                                               \\
	                                        & = \frac{  p_0(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  p_0(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})},                                                                      \\
	                                        & = \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})} \hspace{0.3cm}(\because p_0(\ell) \propto P^\gamma (\ell)).
\end{align}
Taken together, the conditional probability that SGNS \textit{word2vec} actually optimizes is
\begin{align}
	P^{NS}(j\given i) = P_m^{NS}(\vect{u}_j \cdot \vect{v}_{i})  =  \frac{  P^\gamma(j)\exp( \vect{u}_j \cdot \vect{v}_{i} ) }{Z'_i},
\end{align}
where $Z'_i=\sum_{j' \in \mathcal{A}}  P^\gamma(j') \exp(\vect{u}_{j'} \cdot \vect{v}_{i})$.

### 2021-03-09 paper/rebuttal/rebuttal.tex

\bigskip
\thispagestyle{empty}
\vspace{-0.4cm}
\noindent Dear Dr. Sutherland and Referees,\\
\vspace{-0.25cm}

We thank all the referees for their thoughtful and helpful comments and critiques.
We acknowledge that our initial submission had a substantial gap regarding the choice of the \textit{word2vec} model, its connection with the gravity model of mobility, and its evaluation.
While reflecting on these comments and our manuscript, we have made a theoretical breakthrough that addresses the primary issues;
namely, we have discovered \emph{a mathematical equivalence between the \textit{word2vec} (skip-gram with negative sampling) model and the gravity model.}

Furthermore, our subsequent experiments show that our approach's performance is robust, exceeding many other baselines, even direct optimization of the gravity model.
Therefore, with these changes, we are confident that our paper is substantially stronger with a qualitative leap.
Thus, we would like to request a reconsideration of our manuscript.
Again, we are incredibly appreciative of these comments, which provided the insight and motivation needed to make these breakthroughs.

We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:
\vspace{-0.1cm}
\begin{enumerate}
	\itemsep0em
	\item The lack of theoretical justification and grounding for the application of \textit{word2vec} to mobility
	\item The lack of simpler baselines to understand the performance of \textit{word2vec}
	\item The lack of sufficient grounding in the literature of neural embeddings and mobility
\end{enumerate}
\vspace{-0.1cm}
We address the first point by presenting a mathematical equivalence between the Gravity Model of Mobility and the skip-gram negative sampling \textit{word2vec} model.
Namely, we demonstrate that \textit{word2vec}'s objective function is equivalent to the gravity model and thus \textit{word2vec} learns gravity-like relationships between entities, whether it be language or locations.
This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.

For the second point, we have conducted experiments comparing the performance of neural embedding to (\romannum{1}) a singular value decomposition of the mobility network,  (\romannum{2}) a Laplacian eigenmap embedding  (\romannum{3}) a \textit{word2vec} model with matrix factorization,  and  (\romannum{4}) a direct optimization according at the gravity model. We find that the embedding distance from \textit{word2vec} outperforms all baselines, even the direct optimization of gravity law with the multidimensional scaling, in explaining and predicting real-world mobility.

### 2021-03-09 paper/rebuttal/rebuttal.tex

\response{Thank you for this insightful comment!
	We think that there is a great deal of potential in methods like BERT for representing mobility data.
	What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches).
	This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the gravity model of mobility, which explains why it learns such effective gravity-like relationships between entities (see Section 1, this letter).
	We believe hat this new discovery, now included in the manuscript, justifies our use of \textit{word2vec} here.

	We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however, we argue that our contribution is most well-founded, and best serves the scientific community, by working with simpler and more established models (see Section 2, this letter), especially concerning the mathematical link we uncovered. Moreover, these deep models require a tremendous amount of training data ($\sim$3 billion words in Bert) and model parameters, making their use infeasible in applicants most.

@@

\rcomment{
	My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility. The technical description addressed most of them. However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference? That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance? For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects? Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
}

\response{Thank you for this idea!
	We believe that this is an interesting topic and we hope to investigate it in the future.
	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
	This is certainly a topic that is in our mind for future study.
	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.

	However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}, which adds a substantial amount of new results to the manuscript.
}
